AWIPEV-CO2

### 2019-02-11 awipev-CO2.Rmd
path changed figures are now saved in figures folder in not synced rather than on pCloud

ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png"), calib_p, units="cm")
print(calib_p)
```

@@

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
  geom_hline(yintercept = 0, linetype="dashed" )+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     "Slope =",signif(fit$coef[[2]], 5),
                     "P =",signif(summary(fit)$coef[2,4], 5))) + 
  ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png"), p, units="cm")
```

@@

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
  geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
  #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
  scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png"), p, units="cm")
```

@@

ggsave(paste0(path, "fb_figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")

@@

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2calc_pCO2_contros_text)
ggsave(paste0(path, "fb_figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
```

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
ggsave(paste0(path, "fb_figures/SNAPO/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0(path, "fb_figures/SNAPO/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```

>>>>

ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm")
print(calib_p)
```

@@

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
  geom_hline(yintercept = 0, linetype="dashed" )+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     "Slope =",signif(fit$coef[[2]], 5),
                     "P =",signif(summary(fit)$coef[2,4], 5))) + 
  ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
```

@@

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
  geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
  #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
  scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
```

@@

ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")

@@

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2calc_pCO2_contros_text)
ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
```

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```

### 2019-02-11 presentation/awipev-CO2_pres.Rmd
path changed figures are now saved in figures folder in not synced rather than on pCloud

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

@@

![ ](images/Discrete_TA_salinity_AWIPEV.png)

>>>>

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../../pCloud\ Sync/exp168_awipev-CO2/"

@@

![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
